\label{fig:outliers}
\textbf{(a)} The distribution of residuals per uncertainty (\textit{standardized} residuals) between the observed and KT-derived line-of-sight velocities of HMSFRs (filled histogram), with an appropriately scaled standard normal distribution for reference (empty histogram). We consider HMSFRs with $\vert \Delta v / \sigma \vert > 3$ to be outliers. In all three panels, outliers are denoted in orange and non-outliers are denoted in blue. 
\textbf{(b)} The distribution of the HMSFRs' Galactic longitudes. HMSFRs (outliers and non-outliers) with $\glon < 35^\circ$ are outlined with a dashed black line.
\textbf{(c)} The distribution of the HMSFRs' Galactocentric radii. HMSFRs (outliers and non-outliers) with $\glon < 35^\circ$ are outlined with a dashed black line.
\textbf{(d)} The locations of the outliers and non-outliers in heliocentric Cartesian coordinates, where $\mathrm{X_{HC}}$ increases towards $\glon=0^\circ$ and $\mathrm{Y_{HC}}$ increases towards $\glon=90^\circ$. 
\textbf{(e)} The probability of finding m or more of the n=5 total outliers among M=31 HMSFRs drawn at random and without replacement from the full population of N=99. The $\glon < 35^\circ$ subsample contains 31 HMSFRs, total, and 5 outliers. The probability of this happening if an HMSFR's chance of being an outlier is independent of Galactic longitude is well below the $2\sigma$-equivalent threshold of $5\%$.
\textbf{(f)} The same probabilities as in (e), but for N=99, n=5, M=17 (solid lines) and N=31, n=5, M=17 (dashed lines). In both cases, the number M of HMSFRs in the subsample is the number of HMSFRs with $3 \text{ kpc} < \mathrm{R_{GC}} < 5\text{ kpc}$. The N=99 and N=31 cases correspond to the subsample being drawn from the full 99 HMSFR sample and from the $\glon < 35^\circ$ subsample. The N=99 case is clearly inconsistent with outliers being independent of $\mathrm{R_{GC}}$. The probability of the N=31 case is just below the 2$\sigma$ equivalent level, suggesting that the outliers' $\mathrm{R_{GC}}$ values stand out from those of all HMSFRs with $\glon < 35^\circ$.
